R for Clinical Study Reports and Submission

### 2023-05-25 preface.qmd
Migrate from bookdown to Quarto book (working HTML book)
Update authors in metadata and preface

# Preface {-}

@@

  Yilong Zhang <<elong0527@gmail.com>>, Nan Xiao, Keaven Anderson, Yalin Zhu

@@

```{block2, type="flushright", html.tag="p"}
Yilong Zhang, Nan Xiao, Keaven Anderson, Yalin Zhu

December 2022
```

>>>>

# Preface {.unnumbered}

@@

  [Yilong Zhang](https://elong0527.github.io/),
  [Nan Xiao](https://nanx.me/),
  [Keaven Anderson](https://keaven.github.io/),
  Yalin Zhu

@@
